### 2018-10-25 paper/complexity.tex
update

It remains to 
consider the question whether reference processes $Z$ possessing failures $(s,\Sigma)$
may require more test executions for their associated tests $U_F(j)$ than the bound
given for $\pmax$ in (\ref{eq:pmaxcomplexity}). To this end, we consider the following process $Z$ whose behaviour is quite close to that of $\pmax$ with the only difference
that after some pre-defined trace $\ol s \in\Sigma^*$ with $\#\ol s < pq$, 
the process has $\Stop$ as
an internal choice, so that $Z/s = \big(\Intchoice_{A\in{\cal C}} e:A\then \pmax\big) \intchoice \Stop$, and, consequently, $\minhits(Z/s) = \varnothing$.

In the following specification of $Z$, given traces $s_1,s_2\in\Sigma^*$, the Boolean 
expression $ s_1 < s_2$ evaluates to $\ist$ if and only if $s_1$ is a true prefix of $s_2$.
\begin{eqnarray*}
Z & = & Z_1(\varepsilon)
\\
Z_1(s) & = & (s < \ol s)\&\big( \Intchoice_{A\in{\cal C}} e:A\then Z_1(s.e)  \big)
\\ & & \extchoice
\\ & & (s \not< \ol s) \& \pmax
\\ & & \extchoice
\\ & & (s = \ol s) \& \big( \Intchoice_{A\in{\cal C}} e:A\then \max  \big)
\intchoice \Stop
\end{eqnarray*}
%
It is easy to see that $\trc(Z) = \trc(\pmax) =\Sigma^*$ and that for all 
traces $s\neq\ol s$, $\minhits(Z/s) = \minhits(P/s) = \minhits({\cal C})$ as specified
in Lemma~\ref{lemma:pmax}.

>>>>

It remains to 
consider the question whether reference processes $Z$ possessing failures $(s,\Sigma)$
may require more test executions for their associated tests $U_F(j)$ than the bound
given for $\pmax$ in (\ref{eq:pmaxcomplexity}). To this end, we consider an {\it arbitrary} process  $Z$ and study the potential increase of test executions if
the behaviour of $Z$ is changed to $(Z/\ol s)\intchoice \Stop$ after some specific 
trace $\ol s\in\trc(Z)$ with $\minhits(P/\ol s) \neq \varnothing$. This modified process is denoted by $Z({\ol s})$
an can be specified by\footnote{We use the following prefix operators
for given   traces $s_1,s_2\in\Sigma^*$: the Boolean 
expression $ s_1 < s_2$ evaluates to $\ist$ if and only if $s_1$ is a true prefix of $s_2$. Expression $s_1\le s_2$ holds if and only if $ s_1 < s_2 \vee s_1 = s_2$ is true.}
\begin{eqnarray}
Z({\ol s}) & = & Z({\ol s},\varepsilon)
\\
\label{eq:zstop}
Z(\ol s,s) & = & (s = \ol s) \& ((Z/s)\intchoice \Stop)
\\ & & \Extchoice    \nonumber
\\  
\label{eq:zstoppref}
& & (s < \ol s \wedge \minhits(P/s) = \varnothing) \& 
\big(  (e:[P/s]^0 \then  Z(\ol s, s.e)) \intchoice \Stop \big)
\\ & & \Extchoice   \nonumber
\\ 
\label{eq:zcont}
& &           (s < \ol s\wedge \minhits(P/s) \neq \varnothing ) \& 
\\ & & \nonumber
\big(\Intchoice_{A\in\minaccs(P/s)\cup \{ [P/s]^0 \}}
e : A \then Z(\ol s, s.e)          \big)
\\ & & \Extchoice   \nonumber
\\
\label{eq:zlikep}
& & (s \not\le \ol s) \& (P/s)
\end{eqnarray}
%
If $Z(\ol s,s)$ has executed trace $\ol s$, its branch (\ref{eq:zstop}) is entered, 
so the process 
nondeterministically decides whether to continue like $Z/s$ or to stop. As a consequence,
$Z(\ol s)/\ol s = Z(\ol s,\ol s)$ only has $\varnothing$ as minimal acceptance, and its
  collection of minimal hitting sets is empty.
 While $Z(\ol s)$ still executes a true prefix
of $\ol s$, it behaves exactly as $Z$, executing either branch (\ref{eq:zstoppref}) or
(\ref{eq:zcont}): the latter branch is taken if $P/s$ has at least one minimal hitting set,
so that it cannot refuse all elements of $[P/s]^0$. In such a case, $P/s$ can be
represented in a normalised form, where an initial event is selected from an internal
choice over all minimal acceptances and over $[P/s]^0$ (the choice $[P/s]^0$ is needed
because the union over all minimal acceptances is not necessarily identical 
to $[P/s]^0$)~\cite[pp.~277]{Roscoe:1997:TPC:550448}. 
The former branch is taken if $P/s$ can block all of its initials.
As a consequence, in both branches, $Z(\ol s,s)$ 
has the same nondeterministic behaviour and the same initials as $P/s$, as long as
a prefix of $\ol s$ is executed. As soon as $Z(\ol s)$ has run through a trace $s$ that is no longer a prefix of $\ol s$, 
the process continues exactly as $Z$ would do after having run through $s$. This situation
is captured by branch (\ref{eq:zlikep}).
Summarising, $Z(\ol s)$ behaves like $P$ for all but the
one trace   $\ol s$.

% -----------------------------------------------------------------------------
\subsubsection*{Considering Empty Collections of Minimal Hitting Sets -- Old version}

In the following specification of $Z$, given traces $s_1,s_2\in\Sigma^*$, the Boolean 
expression $ s_1 < s_2$ evaluates to $\ist$ if and only if $s_1$ is a true prefix of $s_2$. Expression $s_1\le s_2$ holds if and only if $ s_1 < s_2 \vee s_1 = s_2$ is true.
\begin{eqnarray*}
Z & = & Z_1(\varepsilon)
\\
Z_1(s) & = & (s < \ol s)\&\big( \Intchoice_{A\in{\cal C}} e:A\then Z_1(s.e)  \big)
\\ & & \extchoice
\\ & & (s \not\le \ol s) \& \pmax
\\ & & \extchoice
\\ & & (s = \ol s) \& \big( (\Intchoice_{A\in{\cal C}} e:A\then \pmax)  
\intchoice \Stop\big)
\end{eqnarray*}
%
It is easy to see that $\trc(Z) = \trc(\pmax) =\Sigma^*$ and that for all 
traces $s\neq\ol s$, $\minhits(Z/s) = \minhits(P/s) = \minhits({\cal C})$ as specified
in Lemma~\ref{lemma:pmax}.
